New lower bounds for Schur and weak Schur numbers

### 2021-09-24 article/article.tex
corrections x42

This article provides new lower bounds for both Schur and weak Schur numbers by exploiting a "template"-based approach. 
The concept of "template" is also generalized to weak Schur numbers. Finding new templates leads to explicit partitions 
improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). 
The new lower bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), 
\(\WS (9) \geqslant 22\,536\) and \(\WS (10) \geqslant 71\,256 \).

@@

\qquad First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).

>>>>

This article provides new lower bounds for both Schur and weak Schur numbers by exploiting a "template"-based approach. 
The concept of "template" is also generalized to weak Schur numbers. Finding new templates leads to explicit partitions 
improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and multicolor Ramsey numbers \(R_n(3)\). 
The new lower bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), 
\(\WS (9) \geqslant 22\,536\) and \(\WS (10) \geqslant 71\,256 \).

@@

First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).

### 2021-09-24 article/introduction.tex
abstract + future works + .!!!!
corrections x42

\qquad We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no 
subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
\textit{sum-free}. If we add the hypothesis \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The 
greatest \(p\) for which there exists a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur 
number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\) 
the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Values of \(S(n)\) and \(\WS(n)\) are known for small \(n\) only.

@@

\qquad Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson 
\cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large 
numbers. No equivalent was known for weak Schur numbers and as a result the best known partitions for large 
weak Schur numbers did not use the weakly sum-free hypothesis.

@@

\par
In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which 
generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
He also provides two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
over previous lower bounds. Besides, these two inequalities do use the \textit{weakly} sum-free hypothesis.

@@

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
	& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & 
		\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
	\hline
	\hyperref[Schur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for weak Schur numbers}
\label{table:2}
\end{table}

@@

\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special case 
a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time for \textit{weak} Schur numbers.

@@

\par
In Section \ref{WeakSchur}, we generalize the concept of templates to weak Schur numbers 
and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
lower bound for \(\WS(6)\).

@@

\qquad We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
We denote \(\mathbb{N} = \{0, 1, 2, ...\}\) and \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).

\begin{definition}
A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} if
\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
\end{definition}

\begin{definition}
A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} if
\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
\end{definition}

@@

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\)) 
can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur 
number.
\end{definition}

>>>>

We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no 
subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
\textit{sum-free}. If we add the hypothesis \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The 
greatest \(p\) for which there exists a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur 
number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\) 
the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Values of \(S(n)\) and \(\WS(n)\) are known for small \(n\) only.

@@

Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson 
\cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large 
numbers. No equivalent was known for weak Schur numbers and as a result the best known partitions for large 
weak Schur numbers did not use the weakly sum-free hypothesis.

@@

\par
In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which 
generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
He also provided two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
over previous lower bounds. Besides, these two inequalities do use the \textit{weakly} sum-free hypothesis.

@@

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
	& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & 
		\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
	\hline
	\hyperref[WeakSchur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for weak Schur numbers}
\label{table:2}
\end{table}

@@

Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special case 
a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time for \textit{weak} Schur numbers.

@@

\par
In Section \ref{WeakSchur}, we generalize the concept of template to weak Schur numbers 
and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
lower bound for \(\WS(6)\).

@@

We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
We denote \(\mathbb{N} = \{0, 1, 2, ...\}\) and \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).

\begin{definition}
A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} if
\[ \forall (a,b) \in A^2 \text{, } a+b \notin A.\]
\end{definition}

\begin{definition}
A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} if
\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B.\]
\end{definition}

@@

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\) 
can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur 
number.
\end{definition}

### 2021-09-24 article/schur.tex
abstract + future works + .!!!!
corrections x42

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
is then defined as a new object filling the role of the first line but with less, yet sufficiant, constraints which allow a linear 
expansion of the partition.

\begin{definition}
Let \((p,n) \in (\mathbb{N}^*)^2\). A S-template with width \(p\) and \(n\) colors is defined as a partition of 
\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying for all subsets but \(A_n\)
\[
\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
\Longrightarrow x+y-p \notin A_i
\]
\end{definition}

@@

\begin{proposition}
	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer such that \( [\![1, S^+(n)]\!]\) is a S-template with \(n\) colors. 
	\(S^+(n)\) is well defined and verifies
	\[
	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n)
	\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets. \\
\end{proof}

@@

We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition. We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.

@@

\begin{corollary}
\label{cor:ineqS}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1 \]
\end{corollary}

@@

\textbf{Abbott and Hanson's construction}
\vspace{1.7ex}

@@

\setlength{\tabcolsep}{6pt}
\caption{Visualisation of an Abbott and Hanson construction}
\end{center}
\label{figure:1}
\end{figure}
In the general construction with S-templates, the special color no longer necessarily contains consecutive 
numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
line number and the other colors are still vertically extended.

@@

	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
	\(u\) as the collumn number of \(x\). A new coloring is define as follows:
	\[
	\begin{array}{c c c l}
		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!], \\
		& x & \longmapsto & 
		\left\{ \begin{array}{l l}
			f(u), & \text{if}~f(u) \leqslant n, \\
			n + g(\alpha), & \text{if}~f(u) = n + 1. \\
		\end{array} \right.
	\end{array}
	\]

@@

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
\[ S(n+k) \geqslant S^+(n+1)S(k) + b\].
\end{proposition}
This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened and as a result, we can change the coloring on the last row to extend the previous partitions.
\newline

@@

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k) \].
\end{corollary}

@@

\par
Here are the inequalities given by the current best S-templates. The \hyperref[S-templates]{templates} 
corresponding to the third, fourth and fifth inequalities can be found in the appendix.

\begin{align}
	S(n + 1) \geqslant &~3\,S(n)  + 1 \label{S(n+1)}\\
	S(n + 2) \geqslant &~9\,S(n)  + 4 \label{S(n+2)}\\
	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}\\
\end{align}

@@

@@

Except for \(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
the third inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
doesn't go any further, but the same inequality allows to improve the
lower bounds for every \( n \geqslant 15 \).

>>>>

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
is then defined as a new object filling the role of the first line but with less, yet sufficient, constraints which allow for an 
expansion of the partition using a sum-free partition.

\begin{definition}
Let \((p,n) \in (\mathbb{N}^*)^2\). A S-template with width \(p\) and \(n\) colors is defined as a partition of 
\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying for all subsets but \(A_n\)
\[
\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
\Longrightarrow x+y-p \notin A_i.
\]
\end{definition}

@@

\begin{proposition}
	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there exists a S-template with 
	width \(w\) and \(n\) colors. 
	\(S^+(n)\) is well defined and verifies
	\[
	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n).
	\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
The upper bound comes from the fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) 
into \(n\) sum-free subsets. The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
\end{proof}

@@

We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition. 
We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.

@@

\begin{corollary}
\label{cor:ineqS}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1.\]
\end{corollary}

@@

\textbf{Abbott and Hanson's construction}
\label{figure:1}
\vspace{1.7ex}

@@

\setlength{\tabcolsep}{6pt}
\caption{Visualisation of an Abbott and Hanson construction}
\end{center}
\end{figure}
In the general construction with S-templates, the special color no longer necessarily contains consecutive 
numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
line number and the other colors are still vertically extended.

@@

	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
	\(u\) as the collumn number of \(x\). A new coloring is define as follows:
	\[
	\begin{array}{c c c l}
		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!], \\
		& x & \longmapsto & 
		\left\{ \begin{array}{l l}
			f(u), & \text{if}~f(u) \leqslant n, \\
			n + g(\alpha), & \text{if}~f(u) = n + 1. \\
		\end{array} \right.
	\end{array}
	\]

@@

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
\[ S(n+k) \geqslant S^+(n+1)S(k) + b.\]
\end{proposition}
This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened and as a result, we can change the coloring on the last row to extend the previous partitions.
\newline

@@

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\). Then
	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k).\]
\end{corollary}

@@

\par
The following six inequalities are given by the current best S-templates with \(n \leqslant 7\) colors.

\begin{align}
	S(n + 1) \geqslant &~3\,S(n)  + 1 \label{S(n+1)}\\
	S(n + 2) \geqslant &~9\,S(n)  + 4 \label{S(n+2)}\\
	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}
\end{align}

@@

\par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}) and 
(\ref{S(n+5)}) can be found in the appendix.

@@

Except for \(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
the fifth inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
doesn't go any further, but the same inequality allows to improve the
lower bounds for every \( n \geqslant 15 \).

### 2021-09-24 article/weakschur.tex
abstract + future works + .!!!!
corrections x42

In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
given in this paper.

@@

\begin{proposition}
\label{prop1}
\[
\forall x \in [\![b + 1, a + b]\!], \pi(x) = x
\]
\end{proposition}

@@

\begin{proposition}
\label{prop2}
Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\). Then
\[
\pi(x+\pi(y)) = \pi(x+y)
\]
\end{proposition}

@@

\begin{proposition}
\label{prop3}
Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then
\[
\pi(x+y)=x+\pi(y)
\]
\end{proposition}

@@

\begin{proposition}
\label{prop4}
Let \((x,y)\in (\mathbb{N}^*)^2\). Then
\[
\pi(\pi(x)+\pi(y))=\pi(x+y)
\]
\end{proposition}

@@

\begin{definition}
Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
\end{definition}

@@

\begin{proposition}
\label{prop5}
Let \(x\in \mathbb{N}^*\). Then
\[
x=a\lambda(x)+\pi(x)-a
\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). \\
\(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\)

\begin{itemize}
\item if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
\item if \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
\end{itemize}
\end{proof}

\begin{proposition}
\label{prop6}
Let \(x, y \in \mathbb{Z}\) such that \(\lambda(x + y) = \lambda(y)\). Then
\[
\pi(x + y) = x + \pi(y)
\]
\end{proposition}

@@

\begin{corollary}
Let \(n, k \in \mathbb{N}^*\). Then
\[
\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n)
\]
\end{corollary}

@@

\begin{itemize}
\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!],  \left\{
	\begin{array}{l}
		f(x) = f(y) \\
		\pi(x + y) \leqslant b + c
	\end{array}
	\right. \implies g(\pi(x + y)) \neq f(x)\)
\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!], \left\{
	\begin{array}{l}
		f(x) = g(y) \\
		\pi(x + y) \leqslant b + c
	\end{array}
	\right. \implies g(\pi(x + y)) \neq f(x)\)
\end{itemize}

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have\\
\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
\end{proposition}

@@

\par
Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{templates} 
corresponding to the third inequality can be found in the appendix.

>>>>

In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
we then introduce \textit{WS-templates}, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
given in this paper.

@@

\begin{proposition}
\label{prop1}
\[
\forall x \in [\![b + 1, a + b]\!], \pi(x) = x.
\]
\end{proposition}

@@

\begin{proposition}
\label{prop2}
Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\). Then
\[
\pi(x+\pi(y)) = \pi(x+y).
\]
\end{proposition}

@@

\begin{proposition}
\label{prop3}
Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then
\[
\pi(x+y)=x+\pi(y).
\]
\end{proposition}

@@

\begin{proposition}
\label{prop4}
Let \((x,y)\in (\mathbb{N}^*)^2\). Then
\[
\pi(\pi(x)+\pi(y))=\pi(x+y).
\]
\end{proposition}

@@

\begin{definition}
Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor.\]
\end{definition}

@@

\begin{proposition}
\label{prop5}
Let \(x\in \mathbb{N}^*\). Then
\[
x=a\lambda(x)+\pi(x)-a.
\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). \\
We have \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\).

\begin{itemize}
\item If \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\).
\item If \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\).
\end{itemize}
\end{proof}

\begin{proposition}
\label{prop6}
Let \(x, y \in \mathbb{Z}\) such that \(\lambda(x + y) = \lambda(y)\). Then
\[
\pi(x + y) = x + \pi(y).
\]
\end{proposition}

@@

\begin{corollary}
Let \(n, k \in \mathbb{N}^*\). Then
\[
\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n).
\]
\end{corollary}

@@

\begin{itemize}
\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!],  \left\{
	\begin{array}{l}
		f(x) = f(y) \\
		\pi(x + y) \leqslant b + c
	\end{array}
	\right. \implies g(\pi(x + y)) \neq f(x)\),
\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!], \left\{
	\begin{array}{l}
		f(x) = g(y) \\
		\pi(x + y) \leqslant b + c
	\end{array}
	\right. \implies g(\pi(x + y)) \neq f(x)\).
\end{itemize}

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have\\
\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c.\]
\end{proposition}

@@

\par
Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
corresponding to the third inequality can be found in the appendix.
